The Close Companion Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-03-21 paper/ms.tex
Updated zenodo link

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at the same url, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd}. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.

>>>>

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at \url{https://zenodo.org/record/48073}, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd} and every cross-correlation function generated in our analysis. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.
